\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-17 futurework.tex
add graphs for bwd/fwd

@@

		Compared to forwards exploration, we found that backwards exploration tended to find bugs much more quickly, with fewer backtracks needed before the buggy branch was chosen.
\end{itemize}
% TODO: provide results here
% FIXME: study diffs in trees with no bugs at all

@@

\begin{figure}[h]
	\small
	\centering
	\begin{tabular}{|l||c|c|}
		\hline
		& \texttt{double\_wait} & \texttt{vanish\_vanish} \\
		\hline\hline
		Exploration time & {\bf 30 minutes} & {\bf 5 minutes} \\
		\hline
		Backtracks & {\bf 1,401} & {\bf 1,511} \\
		\hline
		Decision points & 10,355 & 5,690 \\
		\hline
		Average branch depth & 18.34 & 16.00 \\
		\hline
		Average instructions/branch& 1,975,033 & 1,984,249 \\
		\hline
		Total instructions & 206,757,601 & 24,907,516 \\
		\hline
		Backtrack distance minimum & {\bf 6} & {\bf 2} \\
		\hline
		Backtrack distance maximum & 17 & 16 \\
		\hline
		Backtrack distance average & {\bf 7.38}  & {\bf 3.75} \\
		\hline
		% FIXME: add stddev?
	\end{tabular}
	\caption{Comparison of expensive \texttt{double\_wait} test and cheap \texttt{vanish\_vanish} test. The number of branches and depth of each branch are similar, but \texttt{double\_wait}'s backtracks were significantly longer, causing more total instructions to be executed.}
	\label{fig:nadim-stats}
\end{figure}

>>>>

\revision{
\renewcommand\bugnum[2]{#1 {\scriptsize \em (#2)}}
\begin{figure}[t]
	\centering
	\begin{tabular}{cc}
	\multicolumn{2}{c}{\footnotesize
	\centering
	\begin{tabular}{|l|l||c|c|c|}
	\hline
	{\bf Bug} & {\bf Direction} & {\bf Time} & {\bf Backtracks} & {\bf Trace Length} \\
	\hline\hline
	\multirow{2}{*}{POBBLES vanish/vanish (a)} & Forwards & \bugnum{124.8}{4.9} & 1264 & 7 \\
	& Backwards & \bugnum{57.1}{1.7} & 376 & 11 \\
	\hline
	\multirow{2}{*}{POBBLES vanish/vanish (b)} & Forwards & \bugnum{106.3}{5.7} & 1030 & 7 \\
	& Backwards & \bugnum{51.5}{2.1} & 376 & 10 \\
	\hline
	\multirow{2}{*}{POBBLES wait/wait} & Forwards & \bugnum{62.6}{3.4} & 132 & 8 \\
	& Backwards & \bugnum{27.9}{0.8} & 17 & 13 \\
	\hline
	\multirow{2}{*}{POBBLES thread\_fork/vanish} & Forwards & \bugnum{21.4}{0.7} & 0 & 6 \\
	& Backwards & \bugnum{37.4}{1.1} & 70 & 6 \\
	\hline
	\multirow{2}{*}{LudicrOS vanish/vanish} & Forwards & \bugnum{14.7}{0.9} & 4 & 3 \\
	& Backwards & \bugnum{13.7}{0.7} & 3 & 7 \\
	\hline
	\multirow{2}{*}{LudicrOS yield/vanish} & Forwards & \bugnum{13}{0.9} & 3 & 3 \\
	& Backwards & \bugnum{11.4}{0.4} & 0 & 5 \\
	\hline
	\end{tabular}
	}
	\vspace{0.1in}
	\\
	\includegraphics[width=0.48\textwidth]{graphs/backwards-time.pdf} &
	\includegraphics[width=0.48\textwidth]{graphs/backwards-trace.pdf}
	\end{tabular}
	\caption{Comparison of forwards and backwards explorations for the six case study bugs (using decision points on \texttt{mutex\_lock} but not \texttt{mutex\_unlock}). In general, backwards exploration finds bugs faster, but forwards exploration produces shorter (more understandable) decision traces.}
	\label{fig:backwards}
\end{figure}
}

@@

		Compared to forwards exploration, we found that backwards exploration tended to find bugs much more quickly, with fewer backtracks needed before the buggy branch was chosen.
\end{itemize}

\revision{Figure~\ref{fig:backwards} compares the tree explorations and resulting decision traces. The one exception is the POBBLES thread\_fork/vanish bug, which Landslide found immediately during forwards exploration, because the race actually required no forced preemptions to expose.}

@@

\begin{table}[h]
	\small
	\centering
	\begin{tabular}{|l||c|c|}
		\hline
		& \texttt{double\_wait} & \texttt{vanish\_vanish} \\
		\hline\hline
		Exploration time & {\bf 30 minutes} & {\bf 5 minutes} \\
		\hline
		Backtracks & {\bf 1,401} & {\bf 1,511} \\
		\hline
		Decision points & 10,355 & 5,690 \\
		\hline
		Average branch depth & 18.34 & 16.00 \\
		\hline
		Average instructions/branch& 1,975,033 & 1,984,249 \\
		\hline
		Total instructions & 206,757,601 & 24,907,516 \\
		\hline
		Backtrack distance minimum & {\bf 6} & {\bf 2} \\
		\hline
		Backtrack distance maximum & 17 & 16 \\
		\hline
		Backtrack distance average & {\bf 7.38}  & {\bf 3.75} \\
		\hline
		% FIXME: add stddev?
	\end{tabular}
	\caption{Comparison of expensive \texttt{double\_wait} test and cheap \texttt{vanish\_vanish} test. The number of branches and depth of each branch are similar, but \texttt{double\_wait}'s backtracks were significantly longer, causing more total instructions to be executed.}
	\label{fig:nadim-stats}
\end{table}
